A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-12 BSS7782.tex
Update BSS7782.tex

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  We assume circular orbits for both the inner and outer
orbits, and co-planar triples only since this is what has been
observed for low-mass tertiaries \cite{2010yCat..73890925T} \simon{I
  think that {\em moe18} and {\em tobin18} are not the right
  references...NL:  Agreed.  Do you have others to recommend?  These were what came to mind, but 
  I can do some digging to try to find the more appropriate refs.}.  This initial configuration for our assumed formation
scenario for Binary 7782, described below, is depicted in
Figure~\ref{fig:fig1}.

>>>>

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  We assume circular orbits for both the inner and outer
orbits, and co-planar triples only since this is what has been
observed for low-mass tertiaries \cite{2010yCat..73890925T} \simon{I
  think that {\em moe18} and {\em tobin18} are not the right
  references - NL: I am fine with swapping out this figure for another, ultimately.  It still does need work.  Could you send me the files you have for radius as a function of primary mass?  I can then update the figure with that, using your assumed initial masses for the simulations.  That *would* basically finish everything I had intended with the figure, so if we still want to remove it after that, that is totally fine.}.  This initial configuration for our assumed formation
scenario for Binary 7782, described below, is depicted in
Figure~\ref{fig:fig1}.
